Artículo 3. REMD 2019.

### 2022-05-11 Articulo3_LIDE/Draft_Articulo3_LIDE_REMD.Rmd
Nuevas estimaciones de Kaplan Meier y curvas de supervivencia KM estimadas.

>>>>

```{r}
modelo2_KM <- survfit(Surv( (df_analisis_EMA_2014 %>% filter(hijos_rec != 99))$duracion_matrimonio , (df_analisis_EMA_2014 %>% filter(hijos_rec != 99))$evento_divorcio ) ~ (df_analisis_EMA_2014 %>% filter(hijos_rec != 99))$hijos_rec )
modelo2_KM
```

```{r}
summary(modelo2_KM)
```

```{r}
autoplot(modelo2_KM, conf.int = FALSE) + ylab('S(t)') + ggtitle('Curva de Supervivencia de KM Estimada')
```

```{r}
modelo3_KM <- survfit(Surv( (df_analisis_EMA_2014 %>% filter(mcap_bie != 9))$duracion_matrimonio , (df_analisis_EMA_2014 %>% filter(mcap_bie != 9))$evento_divorcio ) ~ (df_analisis_EMA_2014 %>% filter(mcap_bie != 9))$mcap_bie )
modelo3_KM
```

```{r}
summary(modelo3_KM)
```

```{r}
autoplot(modelo3_KM, conf.int = FALSE) + ylab('S(t)') + ggtitle('Curva de Supervivencia de KM Estimada')
```

```{r}
R_divorcios_2014 <- dim(df_analisis_EMA_2014)[1]
nacionalidad_pareja <- rep(0, R_divorcios_2014)

for (i in 1:R_divorcios_2014) {
  if (df_analisis_EMA_2014$nac_hom[i] == df_analisis_EMA_2014$nac_muj[i]) {nacionalidad_pareja[i] = 'Misma nacionalidad'}
  else {nacionalidad_pareja[i] = 'Diferentes nacionalidades'}
}

df_analisis_EMA_2014$nacionalidad_pareja <- nacionalidad_pareja
```

```{r}
modelo4_KM <- survfit(Surv( df_analisis_EMA_2014$duracion_matrimonio , df_analisis_EMA_2014$evento_divorcio ) ~ df_analisis_EMA_2014$nacionalidad_pareja )
modelo4_KM
```

```{r}
summary(modelo4_KM)
```

```{r}
autoplot(modelo4_KM, conf.int = FALSE) + ylab('S(t)') + ggtitle('Curva de Supervivencia de KM Estimada')
```
